\section{First Section}
According to all known laws
of aviation,
there is no way a bee
should be able to fly.
Its wings are too small to get
its fat little body off the ground.
The bee, of course, flies anyway
because bees don't care
what humans think is impossible.\todocite[Page 1]{bee movie script}

Yellow, black. Yellow, black.
Yellow, black. Yellow, black.

Ooh, black and yellow!
Let's shake it up a little.

Barry! Breakfast is ready!

Ooming!

Hang on a second.

Hello?

- Barry?
- Adam?

- Oan you believe this is happening?
- I can't. I'll pick you up.

Looking sharp.

Use the stairs. Your father
paid good money for those.

Sorry. I'm excited.

Here's the graduate.
We're very proud of you, son.

A perfect report card, all B's.

Very proud.

\section{Second Sceriopn}
Barry: 	Between you and me, I was dying to get out of that office.
Adam: 	You have got to start thinking bee, my friend. Thinking bee!
Barry: 	Me?
Adam: 	Thinking bee, thinking bee! Get smart and start thinking bee!
Barry: 	Gee!
Adam: 	Flying here and buzzin' there.
Barry: 	I'm lovin' the views.
Adam: 	Listen to me cousin, every buzzer must use to be a bee!
Barry: 	Or not to be.
Adam: 	Start thinking bee!
Adam: 	Barry, you got no occupation.
Barry: 	What, you mean like pollination?
Adam: 	Hey now! That's thinking bee!
Barry: 	Start thinking bee!
Adam: 	Listen to me fella, ain't you been on a tour? Can't cha' stripes of Black and yella.
Barry: 	I just want to be sure!
Adam: 	To be a bee!
Barry: 	Start thinking bee! Can't I wait and see?
Adam: 	No, Barry that's not to be! Be a busy little bee not a tizzy little bee! 
